### 2011-08-16 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

The latter will come in form of tables containing information regarding the data sets, such their size, known optimum for $\alpha = \beta = 1$ and the numbers of vertices and edges in aforementioned graphs.

@@

We have created 3 sets to use in experiments along with the realistic and converted sets, these are called \jmodule{100-100}, \jmodule{100-200} and \jmodule{100-1000}. Note that the name is always in the form $v-e$.

Also, we will need data of comparably similar characteristics but varying size, to study the effects of size on the run times of experiments. For this reason we created 11 more sets, from \jmodule{0-0} as the trivial one to \jmodule{100-500} as the biggest one. We wanted to keep density the same among these sets, and we picked the $\frac{|E|}{E_{max}}$ density interpretation for this.

@@

\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & TODO \\
  Input data set    & all test data sets \\
  Iterations        & 20 \\
  Pool size         & not applicable \\
  $\alpha$, $\beta$ & not applicable \\
  \hline
\end{tabular}

@@

\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Windows \\
  Input data set    & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}

@@

\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Windows \\
  Input data set    & sized artificial data \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}

@@

\begin{algorithm}
\caption{GLPK: native vs. Cygwin set generation 2}
\label{listing-experiment-glpk-native-vs-cygwin-2}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 20$}
	\FOR{$file \in $ sized artificial data}
    \STATE $ES \gets ES \cup \{file, CH = \jmodule{Glpk}(no\:limit), IH = \emptyset\}$  
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

>>>>

The latter will come in form of tables containing information regarding the data sets, such their size, known optimum % TODO footnote explaining that we got the optimum by running GLPK w/o time limit
for $\alpha = \beta = 1$ and the numbers of vertices and edges in aforementioned graphs.

@@

We have created 3 sets to use in experiments along with the realistic and converted sets, these are called \jmodule{100-100}, \jmodule{100-200} and \jmodule{100-1000}. Note that the name is always in the form $v-e$.\\

All of the experimental data sets mentioned so far, realistic, converted and artificial alike will be referred to as \textit{official test data (sets)}.\\

Also, we will need data of comparably similar characteristics but varying size, to study the effects of size on the run times of experiments. For this reason we created 11 more sets, from \jmodule{0-0} as the trivial one to \jmodule{100-500} as the biggest one. From now on, these will be referred to as \textit{sized test data (sets)}. We wanted to keep density the same among these sets, and we picked the $\frac{|E|}{E_{max}}$ density interpretation for this.

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & TODO \\
  Input data        & all official and sized test data sets \\
  Iterations        & 20 \\
  Pool size         & not applicable \\
  $\alpha$, $\beta$ & not applicable \\
  \hline
\end{tabular}
\bigskip  
\end{center}

@@

Apart from comparing different versions, we shall see how the pure GLPK approach behaves. The first part of this experiment will be limiting the run time, thus making it an instance of Truncated branch \& bound. In this case we will see the dependency between the run time and the quality achieved in it. In the second time we will let GLPK run until optimum is found. We shall see the dependency between input size and run time needed to achieve the optimum.

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Windows \\
  Input data        & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Windows \\
  Input data        & all sized test data sets \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

@@

\begin{algorithm}
\caption{GLPK: native vs. Cygwin set generation 2}
\label{listing-experiment-glpk-native-vs-cygwin-2}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 20$}
	\FOR{$file \in $ sized test data}
    \STATE $ES \gets ES \cup \{file, CH = \jmodule{Glpk}(no\:limit), IH = \emptyset\}$  
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

TODO graph + interpretation. Graph should have its Y axis in log, stress this fact in the text too

@@

%         NB class RandomVsFuzzyVsFidaxStart

Our investigation into various CH will start by comparing \jmodule{FIDAX} from the original article \cite{fidax} to 2 of our trivial randomized hungry heuristics, \jmodule{Random} and \jmodule{Fuzzy}.

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & TODO \\
  Input data set    & all official test data sets \\
  Iterations        & 20 \\
  Pool size         & 10 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}
